Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-16 GWLDCII.tex
not doubling the discussin of successors

In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of \hlfix{any positroid cell in the image of this association.}{I'd like to mildly rephrase this because it sounds like we know exactly which cells have non-empty pre-image, which isn't quite what we proved.} \sanote{changed}

@@

Let $[n]$ denote the set of integers $\{1,\dots,n\}$ with the obvious cyclic and linear orders. Our primary focus is Wilson loop diagrams with $V = [n]$, so in order to simplify the exposition we will often use $i+1$ as shorthand for ``the successor of vertex $i$''. \note{We say this here and then again in the paragraph after length.  Can we discuss how to say it once in a clear and concise way.}

@@

We also impose the convention that all vertices should always be interpreted in terms of the cyclic order on $V$; for example, if $V = [n]$ then $(n,n+3)$ means the propagator connecting edges $3$ and $n$. This viewpoint is beneficial for us since many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, or to short propagators such as $(i,i+2)$, and these behave the same regardless of whether we cross the ``first'' vertex or not; however, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.

>>>>

In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams that map to the same positroid.

@@

Let $[n]$ denote the set of integers $\{1,\dots,n\}$ with the obvious cyclic and linear orders.

@@

We also impose the convention that all vertices should always be interpreted in terms of the cyclic order on $V$.  So, for any $i\in V$ we will use $i+1$ to denote the successor of $i$ in $V$.   In particular, if $V = [n]$ then $(n,n+3)$ means the propagator connecting edges $3$ and $n$. This viewpoint is beneficial for us since many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, or to short propagators such as $(i,i+2)$, and these behave the same regardless of whether we cross the ``first'' vertex or not; however, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.
